ASYMPTOTIC VALIDITY OF THE BAYES-INSPIRED INDIFFERENCE ZONE PROCEDURE:

### 2015-07-02 paper/wish/wsc15paper.tex
small changes to paper before final version is ready

Our second example, illustrated in Figure~\ref{fig: tahi2}, is an unknown variance slippage configuration where the variance of the best alternative is 100 times larger than the variance of the other alternatives. Although Theorem~\ref{t:main} applies only to the known-variance version of BIZ, we conjecture that the unknown-variance version of BIZ should exhibit similar behavior.
In this example, we consider $100$ systems with independent normally distributed samples, where $\mu_{100}=\delta,\mu_{99}=0,\dots,\mu_{1}=0$, $\delta$ is within the interval $[0.1,10]$, and $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1$. We set $n_{0}=15$.
As $\delta$ goes to $0$, we observe that the PCS converges to $P^*$, as it did in the known-variance slippage configuration example.
In this example, we have intentionally chosen $n_0$ to be small, and have chosen a large variance for the best system, to cause BIZ to fail to meet the IZ guarantee for $\delta>0$.
Increasing the parameter $n_0$ typically causes BIZ to meet the IZ guarantee for all $\delta$, and we recommend a larger value of $n_0$ in practice.

@@

\noindent {\bf PETER I. FRAZIER} is an Assistant Professor of the School of Operations Research and Information Engineering at Cornell University, Ithaca, NY.  He holds a Ph.D. in operations research and financial engineering industrial engineering from Princeton University. His research interests include optimal learning, sequential decision-making under uncertainty, and machine learning, focusing on applications in simulation optimization, design of experiments, materials science, e-commerce and medicine. He is the secretary of the INFORMS Simulation Society.
His e-mail address is \email{pf98@cornell.edu}.\\

>>>>

Our second example, illustrated in Figure~\ref{fig: tahi2}, is an unknown variance slippage configuration where the variance of the best alternative is 100 times larger than the variance of the other alternatives. Although Theorem~\ref{t:main} applies only to the known-variance version of BIZ, we conjecture that the unknown-variance version of BIZ should exhibit similar behavior.
In this example, we consider $100$ systems with independent normally distributed samples, where $\mu_{100}=\delta,\mu_{99}=0,\dots,\mu_{1}=0$, $\delta$ is within the interval $[0.1,10]$, and $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1$. We set $n_{0}=15$.
As $\delta$ goes to $0$, we observe that the PCS converges to $P^*$, as it did in the known-variance slippage configuration example.
In this example, we have intentionally chosen $n_0$ to be smaller than the recommended value of 100, and have chosen a large variance for the best system, to cause BIZ to fail to meet the IZ guarantee for $\delta>0$.
Increasing the parameter $n_0$ typically causes BIZ to meet the IZ guarantee for all $\delta$, and we recommend a larger value of $n_0$ in practice.

@@

\noindent {\bf PETER I. FRAZIER} is an Associate Professor of the School of Operations Research and Information Engineering at Cornell University, Ithaca, NY.  He holds a Ph.D. in operations research and financial engineering industrial engineering from Princeton University. His research interests include optimal learning, sequential decision-making under uncertainty, and machine learning, focusing on applications in simulation optimization, design of experiments, materials science, e-commerce and medicine. He is the secretary of the INFORMS Simulation Society.
His e-mail address is \email{pf98@cornell.edu}.\\
